---
title: "read_data"
output: html_document
date: '2022-10-06'
---

## Step 1. Import packages

Most of the popular packages are already installed, no need to install them

- arrow can read and write data in various format such as parquet
- dplyr is a grammar of data manipulation, providing a consistent set of 
  verbs that help you solve the most common data manipulation challenges

```{r}
library(tidyverse, warn.conflicts = FALSE)
```

## Step 2. Read data

Below command will read a local dataset of ratings of different chocolate bars.

```{r}
chocolateData <- read_csv("../data/flavors_of_cacao.csv")
```
### Show the first 5 rows

```{r}
head(chocolateData,5)
```

## Step 3. Clean the data


### Replace space with _ for column names

Some of the column names have spaces in them. This line changes the column names to versions without spaces, which let's us talk about the columns by their names.
```{r}
names(chocolateData) <- gsub("[[:space:]+]", "_", names(chocolateData))
head(chocolateData)
```

### Remove percentage signs

Remove percentage signs in the Cocoa_Percent 

```{r}
chocolateData$Cocoa_Percent <- sapply(chocolateData$Cocoa_Percent, function(x) gsub("%", "", x))
head(chocolateData)
```


## Step 4. View the data

Below code draw a plot with "Review_Date" as the x axis and "Rating" as the y axis

- geom_point(): add a point for each data point
- geom_jitter(): move each point slightly so they don't overlap

```{r}
ggplot(chocolateData, aes(x= Review_Date, y = Rating, color = Cocoa_Percent)) + geom_point() + geom_jitter()+geom_smooth(method = 'lm')
```

```{r}

```